Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms

### 2021-03-05 latex/MPP21/paper.tex
cleaning up bib and adding batch size for NN acc section

The MLP network is composed of 4 fully-connected layers with 784, 300, 300, and 10 nodes, respectively.  
The output layer has one node for each digit 0-9. 
Training is performed using batched stochastic gradient descent with a batch size of \GB{ZZZ}.
APA algorithms were used for the middle multiplication of the network (yielding matrix multiplication dimenions $300\times \GB{ZZZ}\times300$), while the input and output layers use the classical matrix multiplication algorithm. 
One network was trained for 50 epochs for each of the APA algorithms and one was trained using the classical matrix multiplication algorithm.

>>>>

The MLP network is composed of 4 fully-connected layers with 784, 300, 300, and 10 nodes, respectively.  
The output layer has one node for each digit 0-9. 
Training is performed using batched stochastic gradient descent with a batch size of 300.
APA algorithms were used for the middle multiplication of the network (yielding matrix multiplication dimensions $300\times 300\times300$), while the input and output layers use the classical matrix multiplication algorithm. 
One network was trained for 50 epochs for each of the APA algorithms and one was trained using the classical matrix multiplication algorithm.
